\bf\mftitle

### 2011-01-30 doc/jInfer/basicdtd/basicdtd.tex
updated documentation to new type of interval expander in dtd

\subsection{Element content export}
Elements are processed in method \code{elementToString()}, but the real work is done in method \code{regexpToString()}, which takes regexp and recursively converts it to string representation.
But before, whole element is sent to method \code{expandIntervalsElement} of class \code{IntervalExpander}.
Its purpose is to convert intervals on regexp and its children to those, that are representable in DTD.
For example regular expression $(a\{2,5\}, b\{0,2\})$ would be transformed to $(a,a,a?,a?,a?,b?,b?)$.
Class \code{IntervalExpander} works recursively.
First, element is passed to \code{expand\.In\.ter\.vals\.E\.le\.me\.nt}, which does (shortened):
\begin{verbatim}
public Element expandIntervalsElement(final Element treeBase) {
  return new Element(
    treeBase.getContext(),
    treeBase.getName(),
    treeBase.getMetadata(),
    expandIntervalsRegexp(treeBase.getSubnodes()),
    treeBase.getAttributes());
}
\end{verbatim}
It calls private method \code{expandIntervalsRegexp} to handle regexp in that element.
This private method makes big switch according to regexp type.
For $\lambda$, it returns $\lambda$.
Otherwise, it examines interval of regexp in method \code{is\.Sa\.fe\.In\.ter\.val}.
In DTD one can represent $+, ?, \ast$, so safe intervals are $\{1, \infty\}, \{0, 1\}, \{0, \infty\}$ respectively.
If interval is not safe, it has to be expanded.
It is easy to do so, first output $min$-times the regexp itself - that is the minimum occurences, with interval set to $\{1, 1\}$.
Then, if interval is bounded, output $max - min$-times the regexp itself with interval $\{0, 1\}$ - that is optional part.
If it is unbounded, attach the regexp once, with interval $\{0, \infty\}$.

After intervals are expanded, further processing in \code{regexpToString} is divided by big \code{switch} statement of type of regexp.
For $\lambda$, it simply returns \code{EMPY} as string.
Tokens are first examined if they are \code{SimpleData}, if so, string \code{\#PCDATA} is returned.
If not, element name is returned.
If interval of this regexp is different from $\{1, 1\}$, the interval \code{toString()} representation is appended.

>>>>

\subsection{Element content export}
Elements are processed in method \code{elementToString()}.
Whole element regexp is sent to method \code{expandIn\.ter\.vals\.Reg\.exp} of class \code{IntervalExpander}.
Its purpose is to convert intervals on regexp and its children to those, that are representable in DTD.
For example regular expression $(a\{2,5\}, b\{0,2\})$ would be transformed to $(a,a,a?,a?,a?,b?,b?)$.
Class \code{IntervalExpander} works recursively.
Regexp is passed to method \code{expandIntervalsRegexp} to handle regexp in that element.
This method makes big switch according to regexp type.
For $\lambda$, it returns $\lambda$.
Otherwise, it examines interval of regexp in method \code{is\.Sa\.fe\.In\.ter\.val}.
In DTD one can represent $+, ?, \ast$, so safe intervals are $\{1, \infty\}, \{0, 1\}, \{0, \infty\}$ respectively.
If interval is not safe, it has to be expanded.
It is easy to do so, first output $min$-times the regexp itself - that is the minimum occurences, with interval set to $\{1, 1\}$.
Then, if interval is bounded, output $max - min$-times the regexp itself with interval $\{0, 1\}$ - that is optional part.
If it is unbounded and $min$ is zero, attach the regexp once, with interval $\{0, \infty\}$.
If $min$ is nonzero, last regexp in required string gets interval $\{1, \infty\}$.

After intervals are expanded, returned regexp is passed to \code{regexpToString()}, which is divided by big \code{switch} statement of type of regexp.
For $\lambda$, it simply returns \code{EMPY} as string.
Tokens are first examined if they are \code{SimpleData}, if so, string \code{\#PCDATA} is returned.
If not, element name is returned.
If interval of this regexp is different from $\{1, 1\}$, the interval \code{toString()} representation is appended.
